Open-Set Domain Adaptation through Self-Supervision

### 2022-02-09 paper/main.tex
Mockup tables

When employing a multi-head architecture, we need to choose which one of the $|\mathcal{C}_s|$ heads to use for the classification task.
Head $R_{1,j}$ is used by picking $j$ as $\displaystyle j = \arg\max_j {\bf\tilde{y}}_i^s$.

@@

>>>>

When employing a multi-head architecture, we need to choose which one of the $|\mathcal{C}_s|$ heads to use for the classification task.
Head $R_{1,j}$ is used by picking $j$ as $\displaystyle j = \arg\max_j {\bf\tilde{y}}_i^t$.

@@

\subsection{Dataset}
\label{sec:dataset}

Our model is tested on the {\it Office-Home} dataset\cite{OfficeHomeDataset}, which features $65$ classes of images over four different domains: Art (A), Clipart (C), Product (P) and Real World (R).
We set the first $45$ classes to be known while the remaining $20$ are unknown.
After each epoch performed during the domain alignment phase, a validation run is performed on the entire original target dataset.
For each experiment, we report both the best achieved {\it HOS} as $HOS_{Best}$ and the one achieved by the last epoch as $HOS$.
As separation is crucial for the model effectiveness, we also report the computer AUROC score for the first part.

\subsection{Results}
\label{sec:results}
All the 12 source-to-target $S\to T$ shift are considered.
Results are reported separately for each possible mode of execution, Multi-Head ON/OFF and Center-Loss ON/OFF.
Each mode has a specific configuration, please refer to \ref{sec:implementation_and_ablation}.

\begin{center}
  \begin{table}
    \begin{tabular}[h]{||c|c|c||c|c||}
      \hline
      \multicolumn{5}{||c||}{Single-Head, CE Loss} \\
      \hline
      Source & Target & $AUC_{ROC}$ & $HOS$ & $HOS_{Best}$ \\
      S & T & 50\% & 30\% & 30\% \\
      S & T & 50\% & 30\% & 30\% \\
      S & T & 50\% & 30\% & 30\% \\
      \hline
      \hline
      \multicolumn{5}{||c||}{Multi-Head, CE Loss} \\
      \hline
      Source & Target & $AUC_{ROC}$ & $HOS$ & $HOS_{Best}$ \\
      S & T & 50\% & 30\% & 30\% \\
      S & T & 50\% & 30\% & 30\% \\
      S & T & 50\% & 30\% & 30\% \\
      \hline
      \hline
      \multicolumn{5}{||c||}{Single-Head, CE+C Loss} \\
      \hline
      Source & Target & $AUC_{ROC}$ & $HOS$ & $HOS_{Best}$ \\
      S & T & 50\% & 30\% & 30\% \\
      S & T & 50\% & 30\% & 30\% \\
      S & T & 50\% & 30\% & 30\% \\
      \hline
      \hline
      \multicolumn{5}{||c||}{Multi-Head, CE+C Loss} \\
      \hline
      Source & Target & $AUC_{ROC}$ & $HOS$ & $HOS_{Best}$ \\
      S & T & 50\% & 30\% & 30\% \\
      S & T & 50\% & 30\% & 30\% \\
      S & T & 50\% & 30\% & 30\% \\
      \hline

    \end{tabular}
    \caption{\label{tab:resoffoff}Test Caption}
  \end{table}
\end{center}
